Evaluating \Htwo{} and \COtwo{} Network Strategies for the European Energy System

### 2023-12-15 report/submissions/journal/paper/paper.tex
paper: slight improvements to appendix and title

% \title{Assessing \Htwo{} and \COtwo{} Network Strategies in Europe}
\title{Competition and Synergies of \Htwo{} and \COtwo{} Networks in Europe}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{baseline/figures/90_nodes/sequestration_map.png}
    \caption{Maximal sequestration potential per offshore region used as input for all models. Note that in most model runs the regional sequestration potentials are not exploited due the the global limit on sequestration.}
\end{figure}

\subsection{Cost comparison across models}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{full/figures/90_nodes/sankey_diagramm.png}
    \caption{Sankey diagram of the carbon flows in the \hybridmodel{} in the Net-Zero scenario.}
    \label{fig:sankey_diagramm}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{net-negative-0.1/full/figures/90_nodes/sankey_diagramm.png}
    \caption{Sankey diagram of the carbon flows in the \hybridmodel{} in the Net-Negative scenario.}
    \label{fig:sankey_diagramm}
\end{figure}

>>>>

\title{Evaluating \Htwo{} and \COtwo{} Network Strategies for the European Energy System}
% \title{Competition and Synergies of \Htwo{} and \COtwo{} Networks in Europe}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\linewidth]{baseline/figures/90_nodes/sequestration_map.png}
    \caption{Maximal sequestration potential per offshore region used as input for all models. Note that in most model runs the regional sequestration potentials are not exploited due the the global limit on sequestration.}
\end{figure}

\clearpage
\subsection{Cost comparison across models}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=.8\linewidth]{full/figures/90_nodes/sankey_diagramm.png}
    \caption{Sankey diagram of the carbon flows in the \hybridmodel{} in the Net-Zero scenario.}
    \label{fig:sankey_diagramm}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.8\linewidth]{net-negative-0.1/full/figures/90_nodes/sankey_diagramm.png}
    \caption{Sankey diagram of the carbon flows in the \hybridmodel{} in the Net-Negative scenario.}
    \label{fig:sankey_diagramm}
\end{figure}
